Comparison of Terrain Following and Cut Cell Grids with a Non-Hydrostatic Model

### 2015-02-11 msc-publication.tex
start introducing advection results; say how sigma is equivalent to BTF

@@

Following \citet{schaer2002}, a tracer is transported above wave-shaped terrain by solving the advection equation for a prescribed horizontal wind.  This challenges the accuracy of the advection scheme in the presence of grid distortions.  The spatial domain, terrain profile, wind field, tracer, SLEVE scale heights are given by \citet{schaer2002}.  The optimisation of SLEVE by \citet{leuenberger2010} is not used, so the exponent $n = 1$.

@@

>>>>

The sigma coordinate transform of \citet{phillips1957} is equivalent to the BTF coordinate transform since they both decay linearly.  However, since they decay with pressure rather than height, sigma coordinates also change with horizontal variations in pressure.

@@

Following \citet{schaer2002}, a tracer is transported above wave-shaped terrain by solving the advection equation for a prescribed horizontal wind.  This challenges the accuracy of the advection scheme in the presence of grid distortions.  The spatial domain, terrain profile, wind field, tracer, SLEVE scale heights are given by \citet{schaer2002}.  The optimisation of SLEVE by \citet{leuenberger2010} is not used, so the exponent $n = 1$.  A tracer is placed above and to the left of the mountain with a magnitude of 1 at its centre and 0 at the perimeter.

@@

The test was executed on the BTF, SLEVE and cut cell grids, and on a regular grid with flat terrain.  Tracer contours at \(t = \SI{0}{\second}, \SI{5000}{\second}\) and \(\SI{10000}{\second}\) are shown in Figure~\ref{fig:advection-tracer}.  The result from \citet{schaer2002} using a fourth-order centred scheme with sigma coordinates (\ref{fig:advection-tracer}a) is compared with the upwind-biased cubic scheme on (\ref{fig:advection-tracer}b) the BTF grid, and (\ref{fig:advection-tracer}c) cut cell grid.
